Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
fixed minor stuff

\documentclass{article}
\usepackage{url}
\usepackage{longtable}
\usepackage{graphicx}
\title{Word Sense Disambiguation\\
\small{Leveraging the NLTK Toolkit and External Tools}}
\author{
Alec Story
Ansu Abraham
Craig Frey\\
Dustin Tiedemann
Michael Zhu
Thomas Levine
Whitney Foster\\
}

@@

\subsection{Stepwise regression}

@@

\subsection{Graphical methods}
We began by plotting the predictors that seemed most influential in the
stepwise regression.

\includegraphics[width=\textwidth]{pg_0001}
%stepwise graph 1
%classifiert, collocation, cooccurrence  
%Interpret this graph

@@

\includegraphics[width=\textwidth]{pg_0002}

more discussin of graphs

\includegraphics[width=\textwidth]{pg_0003}

\includegraphics[width=\textwidth]{pg_0004}

\subsection{Best Run Results}

\begin{longtable}{l | r r r r r r r}
		&	&	\multicolumn{2}{c}{Fine Grain}	&	\multicolumn{2}{c}{Course Grain}	&	\multicolumn{2}{c}{Mixed}\\
Word	&	Corpus Size	&	Precision	&	Recall	&	Precision	&	Recall	&	Precision	&	Recall\\
\hline
provide.v	&	1094	&	0.906	&	0.015	&	0.938	&	0.015	&	0.922	&	0.015\\
watch.v	&	806	&	0.878	&	0.011	&	0.918	&	0.011	&	0.918	&	0.011\\
remain.v	&	1118	&	0.871	&	0.015	&	0.871	&	0.015	&	0.871	&	0.015\\
hot.a	&	696	&	0.853	&	0.007	&	0.853	&	0.007	&	0.853	&	0.007\\
arm.n	&	2137	&	0.841	&	0.027	&	0.841	&	0.027	&	0.841	&	0.027\\
eat.v	&	1463	&	0.833	&	0.018	&	0.833	&	0.018	&	0.833	&	0.018\\
add.v	&	2148	&	0.806	&	0.026	&	0.806	&	0.026	&	0.806	&	0.026\\
plan.n	&	1353	&	0.797	&	0.016	&	0.835	&	0.017	&	0.835	&	0.017\\
talk.v	&	1174	&	0.797	&	0.014	&	0.797	&	0.014	&	0.797	&	0.014\\
use.v	&	214	&	0.786	&	0.003	&	0.786	&	0.003	&	0.786	&	0.003\\
smell.v	&	874	&	0.784	&	0.01	&	0.804	&	0.01	&	0.804	&	0.01\\
audience.n	&	1637	&	0.768	&	0.019	&	0.96	&	0.024	&	0.904	&	0.023\\
expect.v	&	1275	&	0.756	&	0.015	&	0.756	&	0.015	&	0.756	&	0.015\\
mean.v	&	646	&	0.737	&	0.007	&	0.737	&	0.007	&	0.737	&	0.007\\
appear.v	&	2139	&	0.731	&	0.024	&	0.731	&	0.024	&	0.731	&	0.024\\
express.v	&	887	&	0.731	&	0.01	&	0.769	&	0.01	&	0.769	&	0.01\\
interest.n	&	1489	&	0.728	&	0.015	&	0.728	&	0.015	&	0.728	&	0.015\\
sort.n	&	1566	&	0.728	&	0.017	&	0.88	&	0.021	&	0.853	&	0.02\\
begin.v	&	1478	&	0.723	&	0.012	&	0.723	&	0.012	&	0.723	&	0.012\\
note.v	&	1064	&	0.712	&	0.012	&	0.712	&	0.012	&	0.712	&	0.012\\
receive.v	&	422	&	0.708	&	0.004	&	0.708	&	0.004	&	0.708	&	0.004\\
decide.v	&	982	&	0.705	&	0.011	&	0.705	&	0.011	&	0.705	&	0.011\\
wash.v	&	534	&	0.7	&	0.005	&	0.867	&	0.007	&	0.717	&	0.005\\
climb.v	&	1073	&	0.698	&	0.011	&	0.698	&	0.011	&	0.698	&	0.011\\
degree.n	&	2085	&	0.695	&	0.021	&	0.78	&	0.023	&	0.775	&	0.023\\
bank.n	&	2113	&	0.684	&	0.02	&	0.744	&	0.022	&	0.718	&	0.021\\
ask.v	&	2150	&	0.659	&	0.015	&	0.659	&	0.015	&	0.659	&	0.015\\
rule.v	&	478	&	0.655	&	0.005	&	0.655	&	0.005	&	0.655	&	0.005\\
activate.v	&	1874	&	0.65	&	0.017	&	0.65	&	0.017	&	0.65	&	0.017\\
organization.n	&	905	&	0.648	&	0.009	&	0.778	&	0.011	&	0.75	&	0.01\\
operate.v	&	286	&	0.643	&	0.002	&	0.714	&	0.003	&	0.714	&	0.003\\
hear.v	&	510	&	0.633	&	0.005	&	0.7	&	0.005	&	0.7	&	0.005\\
win.v	&	631	&	0.633	&	0.005	&	0.633	&	0.005	&	0.633	&	0.005\\
shelter.n	&	1604	&	0.63	&	0.013	&	0.63	&	0.013	&	0.63	&	0.013\\
party.n	&	1863	&	0.622	&	0.014	&	0.622	&	0.014	&	0.622	&	0.014\\
source.n	&	527	&	0.607	&	0.004	&	0.607	&	0.004	&	0.607	&	0.004\\
difference.n	&	1841	&	0.604	&	0.014	&	0.637	&	0.015	&	0.632	&	0.015\\
write.v	&	355	&	0.579	&	0.003	&	0.579	&	0.003	&	0.579	&	0.003\\
argument.n	&	1831	&	0.577	&	0.01	&	0.676	&	0.012	&	0.669	&	0.012\\
atmosphere.n	&	1332	&	0.574	&	0.009	&	0.574	&	0.009	&	0.574	&	0.009\\
paper.n	&	1914	&	0.574	&	0.009	&	0.721	&	0.011	&	0.689	&	0.011\\
lose.v	&	574	&	0.552	&	0.004	&	0.552	&	0.004	&	0.552	&	0.004\\
produce.v	&	1496	&	0.538	&	0.012	&	0.538	&	0.012	&	0.538	&	0.012\\
encounter.v	&	1046	&	0.534	&	0.008	&	0.966	&	0.014	&	0.615	&	0.009\\
image.n	&	1176	&	0.508	&	0.008	&	0.508	&	0.008	&	0.508	&	0.008\\
disc.n	&	1633	&	0.488	&	0.005	&	0.488	&	0.005	&	0.488	&	0.005\\
difficulty.n	&	378	&	0.474	&	0.002	&	0.842	&	0.004	&	0.719	&	0.003\\
suspend.v	&	1032	&	0.456	&	0.007	&	0.456	&	0.007	&	0.456	&	0.007\\
treat.v	&	903	&	0.442	&	0.005	&	0.465	&	0.005	&	0.465	&	0.005\\
important.a	&	305	&	0.438	&	0.002	&	0.562	&	0.002	&	0.531	&	0.002\\
miss.v	&	470	&	0.435	&	0.003	&	0.435	&	0.003	&	0.435	&	0.003\\
judgment.n	&	502	&	0.429	&	0.003	&	0.429	&	0.003	&	0.429	&	0.003\\
performance.n	&	1398	&	0.396	&	0.005	&	0.562	&	0.007	&	0.521	&	0.006\\
play.v	&	838	&	0.389	&	0.004	&	0.389	&	0.004	&	0.389	&	0.004\\
different.a	&	796	&	0.378	&	0.004	&	0.556	&	0.006	&	0.489	&	0.006\\
solid.a	&	475	&	0.25	&	0.001	&	0.25	&	0.001	&	0.25	&	0.001\\
simple.a	&	298	&	0.182	&	0.001	&	0.545	&	0.002	&	0.409	&	0.001\\

\end{longtable}

>>>>

\documentclass{article}
\usepackage{url}
\title{Word Sense Disambiguation\\
\small{Leveraging the NLTK Toolkit and External Tools}}
\author{
Alec Story
Ansu Abraham
Craig Frey\\
Dustin Tiedemann
Michael Zhu
Thomas Levine
Whitney Foster\\
}

@@

\subsubsection{Stepwise regression}

@@

\subsubsection{Graphical methods}
We began by plotting the predictors that seemed most influential in the
stepwise regression.

%stepwise graph 1
%classifiert, collocation, cooccurrence  
%Interpret this graph

@@

%stepwise graph 2

more discussion of graphs

%stepwise graph 33

\subsection{Characterization of the top feature combinations}

%Let's get a comparison between our best performer(s) and the baseline
